Phylodynamic inference of contact network parameters through approximate Bayesian computation

### 2016-05-27 doc/thesis/discussion.Rnw
Added some MSM/China stuff

{\color{blue}\uline{
The estimates of the prevalence \gls{I} were largely robust to the choice of
prior on \gls{m}} (\cref{fig:abchpd,fig:abchpdm2}).
\uline{\textcite{niculescu2015recent} reported that 494 new \gls{HIV}
infections were diagnosed among the studied population (\glspl{IDU} in
Bucharest) during the study period. Our estimate of the prevalence was higher
(X), although the 95\% \gls{HPD} interval did contain the value 494. In
addition, it is not unreasonable to imagine that a substantial fraction of the
\gls{HIV}-positive individuals in an \gls{IDU} population could be undiagnosed,
given that these populations are often marginalized.

The individuals sampled by \autocite{wang2015targeting} were recruited by
following a prospective cohort of 2000 \gls{MSM} in Beijing. Of the 2000, 179
new infections were identified during the study period. This number is much
lower than the estimated prevalence of X obtained with \software{netabc}.
However, although \citeauthor{wang2015targeting} ... TODO

\textcite{cuevas2009hiv} reported that 620 newly infected and 1500
chronically infected patients had been sampled during the study period, for a
total of 2120. This is substantially greater than the point estimate of X we
obtained with \gls{ABC}, even without considering the likely possibility that
there were more infected than sampled individuals. Again, this error may in
part be due to model misspecification, which highlights the importance of
selecting a model appropriate to the dataset at hand.

}}

>>>>

{\color{blue}\uline{
The estimates of the prevalence \gls{I} were largely robust to the choice of
prior on \gls{m}} (\cref{fig:abchpd,fig:abchpdm2}).
\textcite{niculescu2015recent} \uline{reported that 494 new HIV infections were
diagnosed among the studied population (\glspl{IDU} in Bucharest) during the
study period. Our estimate of the prevalence was higher (X), although the 95\%
\gls{HPD} interval did contain the value 494. In addition, it is not
unreasonable that a substantial fraction of the \gls{HIV}-positive individuals
in an \gls{IDU} population could be undiagnosed, given that these populations
are often marginalized.}

\uline{The individuals sampled by \autocite{wang2015targeting} were recruited by
following a prospective cohort of 2000 \gls{MSM} in Beijing, China. Of the
2000, 179 new infections were identified during the study period. This number
is much lower than the estimated prevalence of X obtained with
\software{netabc}, however the authors did not claim to have sampled the entire
sexual network. In a nationwide survey, \textcite{wu2013hiv} estimated that
there were 24,198 \gls{MSM} living in Beijing, of whom 5.7\%, or 1379, were
\gls{HIV}-infected, which is within the 95\% confidence interval of our
estimate of \gls{I}.}

\uline{\textcite{li2015hiv} studied an \gls{MSM} population in Shanghai, China.
Despite the apparent similarity to the context of the
\textcite{wang2015targeting} study, the estimated \gls{HIV} prevalence of the
\citeauthor{li2015hiv} data was higher (X). The aforementioned
survey~\autocite{wu2013hiv} estimated that there were 14,511 \gls{MSM} living
in Shanghai, with an \gls{HIV} prevalence of 6.8\% or approximately 987
individuals. This was within the 95\% confidence interval of the estimate
obtained with \software{netabc}. It is worth noting that \citeauthor{li2015hiv}
claimed that there were 80,000 \gls{MSM} living in Shanghai, which is a
significantly different estimate than that obtained by \textcite{wu2013hiv}.}

\textcite{cuevas2009hiv} \uline{reported that 620 newly infected and 1500
chronically infected patients had been sampled during the study period, for a
total of 2120. This is substantially greater than the point estimate of X we
obtained with \gls{ABC}, even without considering the likely possibility that
there were more infected than sampled individuals. Again, this error may in
part be due to model misspecification, which highlights the importance of
selecting a model appropriate to the dataset at hand.}
}
